### 2025-06-06 sections/languages.tex
Update languages.tex

\cvskill
{Languages} 
{\textcolor{black}{Spanish (native speaker), English (fluent), Portuguese (advanced reading skills), Italian}}

\cvskill
{} 
{\textcolor{black}{(elemental reading skills), French (elemental reading skills)}} \\

>>>>

\cvskill
{Languages} 
{\textcolor{black}{Spanish (native speaker), English (fluent), Portuguese (advanced reading skills), Dutch,}}

\cvskill
{} 
{\textcolor{black}{French and Italian (elemental reading skills)}} \\
